Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-22 docs/report/report.tex
more edits to related work

For perception existing solutions use a variety of simple to complex techniques. In \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.

A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}. However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

>>>>

From the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor. In the work of Kim, 2014 \cite{Kim2014} a basic color threshold technique was to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide the state estimations. In the work of Heriesse Et al. \cite{Herisse2012} an optical flow technique was applied to a series of images captured on board the quadrotor to estimate the require state estimation in order to control the quad rotor and conduct autonomous landing. While both of these techniques have been shown to work in very specific cases both require case specific parameters to be applied ahead of time, thereby limiting there general applicability.

In the case of Ling \cite{Kim2014}, the brightness used in his thresholding techquie must be set ahead of time and is sensitve to lighting changes and a similar issue is noted in the work of Heriesse \cite{Herisse2012}. Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and the issue of the AprilTags falling out of view of the camera during the final stages of decent were not addressed. This means that as the quadrotor approach the landing pad, it tends to lose any measurements of its state and therefore must complete the final landing procedure by propagating the last measured state forward.

From the controls perspective the majority of literature either uses a set of PID or a Linear Quadratic Controller (LQC) controllers to command and control the quadrotor at all stages of flight based on the state estimation provided by the perception techniques. An LQC was thoroughly explored in \cite{Friis2009} but the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.
